Assessing United States county-level exposure for tropical cyclone impact research

### 2020-07-18 ehp_revision/response_to_reviewers.Rmd

---
title: "Response to reviewers' comments for *\"Assessing United States county-level exposure for research on tropical cyclones and human health\"*"
output: bookdown::pdf_document2
toc: false
bibliography: writing/hurr_exposure.bib
header-includes:
- \usepackage{xcolor}
- \usepackage{framed}
- \usepackage{bm}
- \usepackage{subcaption}
- \usepackage{gensymb}
- \renewcommand\familydefault{\sfdefault}
- \usepackage{sansmath}
- \usepackage{bm}
- \usepackage{soul}
- \sansmath
- \usepackage{booktabs}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{pdflscape}
- \usepackage{float}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{fullpage}
- \usepackage{pdflscape}
- \usepackage{tcolorbox}
- \tcbuselibrary{skins,breakable}
- \usepackage{amsmath}
- \usepackage{xtab}
- \usepackage{rotating}
- \allowdisplaybreaks
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r}
library(knitr)
```

@@

- Ecological fallacy vs individual fallacy, especially in the disaster context
- Spatial misalignment / ecological effects of aggregating data at the county
(or other geopolitical) level. 
- Could be particularly problematic in some high-risk areas, because of the 
"long and narrow" characteristics of island counties. Dare County, Key West.

We think this is a very interesting question for disaster epidemiology, as
while there remains potential for ecological bias, the potential pathways for
health effects may also pass through damage in the individual's community beyond
their residence. For example, damage to major roads in the community might make
it harder for many residents to reach medical care in the aftermath of the
storm, even if their home did not experience extensive destruction. Similarly,
since power is provided over a network, conditions in an individual's community
can be important in determining risk of long-term outages (does Seth have
something on this?). As another example, if hospitals in the community are 
over capacity or have to evacuate, this could increase health risk for people in 
a fairly large "catchment" area for that hospital.

Therefore, while we agree that individual-level data would in many cases be 
helpful for tropical cyclone epidemiology, the ideal might be to design studies 
that integrate both community-level and individual-level metrics of exposure. 
This could help in determining if there are risks introduced to individuals based
on storm-related hazards in their broader community, after controlling for the 
hazards experienced directly at their homes.

There is already some discussion on this topic in the Discussion [exposure 
measurement error / misclassification].

There are two interrelated mechanisms at play regarding this question. The
first is the potential for ecological bias. This bias results from inferring
individual-level associations from data that is available at an aggregated level. 
In the case of epidemiological research, these data include health outcomes, 
exposure, and covariates if the model is adjusting for confounding from them.
For example, in tropical cyclone epidemiology, an ecological study might 
compare county-wide rates of COPD hospitalizations to county-wide measures
of tropical cyclone exposure while controlling for county-level smoking 
rates and age distribution. The model in this case is fit at the county level, 
and so the relevant inference is at that level. If this county-level estimate
is inferred to represent the individual-level association between tropical 
cyclone exposure and risk of COPD hospitalization, controlled for smoking and
age, then the possibility of ecological bias arises. Given that this bias
results from inferring from a model with data at one level of aggregation
to another, this bias is also called cross-level bias.

There are some subtleties that arise regarding this question for disaster
epidemiology. First, it has been argued that, for some ambient exposures
like weather and air pollution, contextual effects (that is, at the community
level) are helpful to estimate in their own right, not just as a potential 
surrogate for individual-level associations. This is because regulations
(in the case of pollutants), interventions, and planning often happen at
this level.

Second, for a disaster, the relevant exposure might be not just at the
individual level (e.g., winds or flooding at the individual's residence), but
also throughout a broader area surrounding the individual. If storm damage
closes roads in a county, for example, or damages the power grid, then these
could create pathways for health risks for individuals throughout the county,
whether damage was high at their residence or not. The causal pathways for
tropical cyclones to affect human health differ from those for a dangerous
substance, like air pollutants, in which the substance itself must enter the
body to cause harm. While some health risk comes directly from the storm (e.g.,
deaths and injuries from trees falling on homes or drowning from flooding),
there are many more pathways that are indirect. These include pathways that go
through the way that the storm's damage affects community infrastructure and
access to medical care. Several papers have discussed the potential for 
"individualistic fallacy", as a counterpoint to "ecological fallacy", when 
such contextual-level exposure pathways are ignored.

There are study designs that can be used to leverage ecological data while 
minimizing risk from ecological bias. For example, potential confounders
like age distribution and smoking rates vary much less within a county over
time than comparing between counties. The mechanism for ecological bias 
depends on the joint distribution between individual exposure, outcome, and 
covariates, if any are included in the model. Time series-style study designs, 
which compare a county to itself over time, allow for very similar covariate
distributions between exposure and non-exposure. Other studies add to this
design by stabilizing for temporal confounding through the addition of 
counties that were never exposed, allowing for a differences-in-differences
style approach to calibrate for seasonal or longer-term trends that might
otherwise create confounding. For example, many health outcomes have a strong
seasonal trend, with peak rates in the winter and lows in the summer. Since
the hurricane season stretches from summer into fall, a study design that compares
the rate of a health outcome in an exposed county to the rate two weeks before
the exposure might be biased away from the null, since baseline rates of the
health outcome will typically be moving up over most of the hurricane season.

Also, there may be confounders that are relevant at the contextual, rather than
individual level, as well as modifiers. Example: whether the county is coastal
could be a contextual-level confounder and effect modifier. This will influence
whether the county is exposed to that storm or not, since storms usually weaken
rapidly when the center is over land. In terms of counfounding pathways, coastal
communities might tend to have lower levels of air pollution, because sea
breezes clear the pollution regularly. They might also be wealthier on average,
since property on or near the beach is desirable. Finally, they might be better
prepared for or more hardened against tropical cyclones at the community-wide
level (e.g., through hardier power infrastructure, more rigorous building codes,
higher likelihood of evacuating in advance of a threatening storm) compared to
nearby inland counties.

Other approaches have also been suggested to reduce ecological bias while 
leveraging ecological data, which might be available at a much larger scale---and
so provide more power---than is practical in collecting individual data. These
include multi-level approaches in which individual-level data from a sample
of individuals in each community is incorporated.

The second issue is exposure measurement error/misclassification. When the 
exposure (e.g., binary exposure or continuous measure of intensity of exposure)
is only measured at the county level, all the individuals in that county are 
assigned that same exposure. However, the hazards included in this study will 
vary across each county. For some hazards, this variation will be more stark. 
For example, tornadoes can be very local, causing extreme damage to a row of 
homes and none to the homes across the street. Some types of floods can also 
be very localized, rather than creating widespread flooding throughout 
the county. In both cases, when a county-level exposure assessment is made
based on an event in the county in association with the storm, there may be
many individuals in the county who did not experience that hazard at their 
residence. The other hazards we included---storm-associated winds and rainfall---will
also have some variation across counties, but this will often not be as stark. 
The rainfields for tropical cyclones are very large, and while there are rainbands
within the storm that might have particularly high rates of precipitation, these
progess over the course of the storm, and it is unlikely that a county will have
one area that experienced very extreme precipitation while another experienced
very little. Winds might have more variation, especially in coastal counties and 
counties near the storm's central track, since winds decay quickly as you move
from the storm's center, and storms typically weaken rapidly once they make 
landfall and can no longer draw on warm ocean waters for energy.

@@

**Response:**

Thank you for this suggestion. We have changed the wording in this sentence:

> **Text in revised manuscript (relevant change in bold):**
"In many cases, these studies analyze multi-year, multi-community data, allowing
them to estimate average associations over many disasters and to explore how a
disaster’s characteristics, or the characteristics ofthe **affected
communities**, modify associated health risks (e.g., Anderson and Bell 2010; Son
et al. 2012; Liu et al. 2017)."

We also used the word "Hits per county per decade" in the legend for Figure 5 in
the main text and Figure S3 of the Supplemental Material. We have revised the
wording in these figures to "Exposures per county per decade".

```{r fig5, fig.cap="Reproduction of Figure 5 from the original manuscript (left) and revised version in the resubmitted manuscript (right). In the revised version, the figure legend was changed from '\\textbf{Hits} per county per decade' to '\\textbf{Exposures} per county per decade' (bold used to highlight change). Figure caption in the revised manuscript: \\textit{Figure caption.}", fig.show = "hold", out.width="40%", fig.align = "center"}
include_graphics("../figures/averageexposureonly.pdf")
include_graphics("figures/averageexposureonly.pdf")
```

@@

> "From Abbe's perspective, however, the full potential for dynamic weather
prediction would not be achieved without standard time worldwide."
[@willis2006cleveland]

> "The time in all hydrometeorological products is expressed according to 
a single standard, which is the Universal Coordinated Time (UTC) 
(formerly known as Greenwich Mean Time [GMT] or Zulu (zero) Time [Z])."
[@usnwstime]

> "The U.S. National Weather Service base all data and product times on the 
UTC standard. ... A common practice is to include a time of the observation 
or event denoting the time with a following capital letter 'Z' to indicate the 
time as UTC." [@usnwstime]

> "The extent and the hour of the observations changed over time. Originally the
observers took the readings at 0735, 1635, and 2335, Washington time, but the
last reading was soon changed to 2300 so that the information could be included
in the morning newspapers. Before the introduction of standard time and time
zones within the United States, a confusing multiplicity of local times existed.
In 1870 there were over 100 such regional times. For the purposes of the
meteorological observations, observers used Washington time until 1885.
Thereafter the observers took their readings according to eastern time, or that
at the 75th meridian west of Greenwich, England. Observers also made local-time
readings from 1876 to 1881.[30]" [@raines1996getting]

> "Once the observers had gathered the weather data, the means of reporting and
disseminating it became most important. Like the Smithsonian, the chief signal
officer made arrangements with the leading commercial telegraph companies to
carry the tri-daily reports. Civilian telegraph experts established special
circuits routed to the Signal Office. The initial arrangement with Western Union
regarding transmission was only temporary, and at the end of the trial period
the company refused to continue service. The House Appropriations Committee held
hearings over the dispute and ruled that the company had a mandate to transmit
the weather information as government business. The Signal Corps compensated the
company, however, at rates determined by the postmaster general.[34]" [@raines1996getting]

> "When making the daily telegraphic reports, the weather observers used special
codes to reduce their length to twenty words in the morning and ten in each of
the other two reports, thereby saving the government both time and money.[35]
Regular transmission of the reports began at 0735 on 1 November 1870 from
twenty-four stations stretching from Boston, Massachusetts, south to Key West,
Florida, and west to Cheyenne in the Wyoming Territory. In addition to the
station atop Mount Washington (opened in December 1870), the Signal Corps soon
reached new heights in weather reporting with the station on Pikes Peak that
began reporting in November 1873.[36]" [@raines1996getting]

> "To provide a picture of weather conditions across the country, the observers
made their reports as nearly simultaneous as possible. The weather service did
not initially make forecasts, and the enabling legislation did not specifically
call for it to do so. Eventually general forecasts, referred to as
probabilities, emanated from the Signal Office in Washington. Locally, the
observers posted bulletins and maps in the offices of boards of trade and
chambers of commerce to provide weather information to the public. Post offices
also displayed daily bulletins, and observers supplied local newspapers with
data. Some communities appointed meteorological committees to confer with the
chief signal officer and to serve as a check upon the operations of the local
weather station. On the national level, the Signal Office in Washington issued
daily weather maps compiled from the reports received from all the stations. It
also published the Daily Weather Bulletin, Weekly Weather Chronicle, and the
Monthly Weather Review. All were available for sale to the public. Myer
estimated that through these various means at least one third of American
households received the Signal Corps' weather information in some form. A
railway bulletin service, initiated in 1879, enabled stations along many major
railroads to display weather information.[37]" [@raines1996getting]

> "The Signal Corps' telegraph network soon expanded beyond the eastern
seaboard. In 1874 Congress enacted legislation directing the War Department to
build lines to connect military posts and protect frontier settlements in Texas
against Indians and Mexicans. Other acts authorized lines in Arizona and New
Mexico and, somewhat later, the Northwest. These lines were intended to serve
sparsely settled areas where commercial lines were not yet available. For the
most part, soldiers maintained and operated the lines, but the Corps employed
some civilians. As the telegraph extended its reach, the weather system also
grew, because the operators doubled as weather observers." [@raines1996getting]

> "Until 1934 the Weather Bureau offices operated 12--15 hours a day with two
basic observations taken at 8 a.m. and 8 p.m. The observations were transmitted
via telegraph. There were no satellite images and few upper air observations."
\url{https://www.weather.gov/dvn/armistice_day_blizzard}

@@

We have added text to clarify the meaning of "synoptic times" in the text:

> **Text in revised manuscript (relevant change in bold):**
"We used tracking data from HURDAT2, which records the storm center’s position
at **four standardized times for weather data collection (synoptic times),**
6:00 am, 12:00 pm, 6:00 pm, and 12:00 am Coordinated Universal Time (UTC)."

\begin{shaded}
\textbf{R3 Comment 3:}
Several of the exposures are calculated for the population mean center of each
county. From the reference list, it looks like the authors consistently used
population centers from 2010 throughout the years included in the dataset/R
package. If so, I suggest clarifying this in the text. 
\end{shaded}

@@

**Response:**

\begin{shaded}
\textbf{R3 Comment 4:}
In the methods section starting on line 276, the authors describe the flooding
and tornado data from the NOAA storm events database. I'd suggest providing some
information about where the events in this database come from (e.g., that they
are reported events) here in addition to covering it in the discussion.

@@

\textit{Lines 276--281 from original manuscript:}

\begin{quotation}
\noindent
\textit{"To identify flood- and tornado-based tropical cyclone exposures in US
counties, we matched storm tracks with event listings from the National Oceanic
and Atmospheric Administration (NOAA)’s Storm Event Database (NOAA NCEI 2020).
While this database has recorded storm data, particularly tornadoes, since 1950,
its coverage changed substantially in 1996 to cover more types of storm events,
including flood events (NOAA NCEI 2020). We therefore only considered flood
metrics of tropical cyclone exposure for storms in 1996 and later."}
\end{quotation}
\end{shaded}

**Response:**

\begin{shaded}
\textbf{R3 Comment 5:}
Line 294: What is meant by the phrase "traditional tornado event database"?

@@

The NOAA Storm Events database originated as a database for recording tornadoes
[? anything else] in the US in 195[x], and was originally called ... . The
database has gone through a number of expansions to cover more events, and it
now includes reports of other types of [hydrometeorological?] disaster events,
including floods, extreme heat and cold, wildfires, frost, hail, ... . However,
it has maintained its status as the database of record [?] for tornadoes in the
United States.

Examples of research papers that leverage this database as a record of tornado
events, or the version of it shared by the [Severe Storm ...] through their
website [ref], include ... .

[Is this database used to validate tornado forecasts / warnings?]

This database has evolved through several stages but has, since its earliest
iteration in the 1950s, served as the National Weather Service's [?] data of
record on tornado events. While there is also a database maintained by the 
[Severe Storm ...], the two databases have different names but almost 
identical information once data are aggregated to a daily, county-level 
measure of whether there was a tornado recorded in that county on that date. 
[Difference between the two and why there are two.]

There is no other tornado base at the same temporal and spatial scale that
we could use for validation.

This database serves as the basis for much of the large-scale (e.g., assessing
patterns over the US over long time periods) tornado-based research for the US. 
It does have some well-documented limitations. One is a notable increase over 
time in the number of tornadoes reported, particularly for the weakest, F0 [?]
tornadoes. [This stabilizes some in the age of radar?]

\begin{shaded}
\textbf{R3 Comment 6:}
Table 1: I suggest providing the rationale for picking the thresholds for
classifying continuous exposures into binary ones within the table. 
\end{shaded}

@@

**Response:**

Wind: gale force?

Precipitation:

Distance:

\begin{shaded}
\textbf{R3 Comment 7:}
Figure 3: The x-axis refers to one of the two wind data sources as "Extended
Best Tracks." Is this the same thing as the wind radii dataset described in the
text? Is so, I suggest clarifying this in the figure label.
\end{shaded}

@@

**Response:**

We have revised the x-axis on the figure to clarify that the comparison is based
on the wind radii dataset described in the text, as requested. The original and
revised versions of this paper are reproduced in this response document as
Figure \@ref(fig:fig3).

[Also revise figure legend?]

```{r fig3, fig.cap="Reproduction of Figure 3 from the original manuscript (left) and revised version in the resubmitted manuscript (right). In the revised version, the x-axis has been labelled to clarify that this axis is showing results based on the wind radii dataset described in the text, in response to Reviewer 3's Comment 7. The revised version also uses a more focused range for the x axis, as requested in EHP's Request 1. Figure caption in the revised manuscript: \\textit{Figure caption.}", fig.show = "hold", out.width="50%"}
include_graphics("../figures/windcomparison.pdf")
include_graphics("figures/windcomparison.pdf")
```

@@

# Requests from EHP: {-#requests-from-ehp}

\begin{shaded}
\textbf{EHP Request 1:}
Figure 3: Please truncate x-axis scale as you do for Figure S7. Since smallest
value is $\sim75\%$, this would make the data in the relevant range much easier to
appreciate.
\end{shaded}

**Response:**

[Typo here? I don't think there's a Figure S7.]

We have revised this figure to show an x-axis truncated at the minimum observed 
value ($\sim75\%$), as requested. The original and revised versions of this paper 
are reproduced in this response document as Figure \@ref(fig:fig3).

@@

\begin{shaded}
\textbf{R2 Comment 2:}
Main text figures (general)
To ensure that figures are accessible to readers with impaired color vision, do not use color as the sole means of conveying information in a figure unless absolutely necessary. Use different symbols, shading/textures, and line patterns instead of (or in addition to) color to distinguish among different data points. Use contrasting colors that can be easily distinguished from each other when the figure is printed in black and white. For details, see: \url{https://ehp.niehs.nih.gov/authors/figures}.
\end{shaded}

**Response:**

In all these figures, we have used a color scale that is both accessible to readers
with the most common forms of impaired color vision and can be easily distinguished 
when the figure is printed in black and white.

For these figures, we selected a color palette that was created to meet both these
criteria. [More on viridis]

In Figure [x] of this response document, we have reproduced the current version of 
each figure as it would appear to someone with [vision impairment].

### 2020-07-18 ehp_revision/response_to_reviewers.Rmd

In Figure [x] of this response document, we have reproduced the current version of 
each figure as it will appear when printed using grayscale (i.e., with most black and 
white printers).

```{r fig5check1, fig.cap="Reproduction of revised version of Figure 5 to check accessibility to readers with two types of colorblindness, deuteranopia (left) and protanopia (right).", out.width="90%", fig.align = "center"}
include_graphics("figures/averageexposureonly_check1.pdf")
```

```{r fig5check2, fig.cap="Reproduction of revised version of Figure 5 to check accessibility to readers with a third type of colorblindness, tritanopia (left) and for printing the figure in grayscale (right).", out.width="90%", fig.align = "center"}
include_graphics("figures/averageexposureonly_check2.pdf")
```

@@

\begin{shaded}
\textbf{R2 Comment 3:}
Figure 3: Please check the contrast between the colors used to indicate numbers
of counties. If you can see the gradient when printed in black and white it
should be ok, but some of the differences are very subtle. Truncating the x-axis
might help with this (if possible.)
\end{shaded}

**Response:**

As we note in our response to the previous comment, we used a color palette
designed to be perceptible both for those with common types of color blindness
and when printed in grayscale. We have increased the size of the circles in
Figure 3 of the revised manuscript (reproduced in Figure \@ref(fig:fig3) of this
response) so that the colors are clearer, as well as truncated the x-axis as
requested in EHP Request 1. Also, we show in Figures \@ref(fig:fig3check1) and
\@ref(fig:fig3check2) of this response how the revised Figure 3 would look with
three common types of color blindness as well as when printed in black and
white. The gradient is clear when this figure is printed in black and white.

```{r fig3check1, fig.cap="Reproduction of revised version of Figure 3 to check accessibility to readers with two types of colorblindness, deuteranopia (left) and protanopia (right).", out.width="100%"}
include_graphics("figures/windcomparison_check1.pdf")
```

```{r fig3check2, fig.cap="Reproduction of revised version of Figure 3 to check accessibility to readers with a third type of colorblindness, tritanopia (left) and for printing the figure in grayscale (right).", out.width="100%"}
include_graphics("figures/windcomparison_check2.pdf")
```

### 2020-07-19 ehp_revision/response_to_reviewers.Rmd

**Response:**

[Typo here? I don't think there's a Figure S7.]

We have revised this figure to show an x-axis truncated at the minimum observed 
value ($\sim75\%$), as requested. The original and revised versions of this paper 
are reproduced in this response document as Figure \@ref(fig:fig3).

\begin{shaded}
\textbf{EHP Request 2:}
Main text figures (general)
To ensure that figures are accessible to readers with impaired color vision, do not use color as the sole means of conveying information in a figure unless absolutely necessary. Use different symbols, shading/textures, and line patterns instead of (or in addition to) color to distinguish among different data points. Use contrasting colors that can be easily distinguished from each other when the figure is printed in black and white. For details, see: \url{https://ehp.niehs.nih.gov/authors/figures}.
\end{shaded}

@@

**Response:**

In all these figures, we have used a color scale that is both accessible to readers
with the most common forms of impaired color vision and can be easily distinguished 
when the figure is printed in black and white.

For these figures, we selected a color palette that was created to meet both these
criteria. [More on viridis]

We have shown an example with one of the figures in the manuscript that uses
this scale. In Figures \@ref(fig:fig5check1) and \@ref(fig:fig5check2) of this
response document, we have reproduced the current version of Figure 5 as it
would appear to someone with three common types of color blindness as well as
when printed using grayscale (i.e., with most black and white printers).

@@

```{r fig5check1, fig.cap="Reproduction of revised version of Figure 5 to check accessibility to readers with two types of colorblindness, deuteranopia (left) and protanopia (right).", out.width="90%", fig.align = "center"}
include_graphics("figures/averageexposureonly_check1.pdf")
```

```{r fig5check2, fig.cap="Reproduction of revised version of Figure 5 to check accessibility to readers with a third type of colorblindness, tritanopia (left) and for printing the figure in grayscale (right).", out.width="90%", fig.align = "center"}
include_graphics("figures/averageexposureonly_check2.pdf")
```

\begin{shaded}
\textbf{EHP Request 3:}
Figure 3: Please check the contrast between the colors used to indicate numbers
of counties. If you can see the gradient when printed in black and white it
should be ok, but some of the differences are very subtle. Truncating the x-axis
might help with this (if possible.)
\end{shaded}

@@

As we note in our response to the previous comment, we used a color palette
designed to be perceptible both for those with common types of color blindness
and when printed in grayscale. We have increased the size of the circles in
Figure 3 of the revised manuscript (reproduced in Figure \@ref(fig:fig3) of this
response) so that the colors are clearer, as well as truncated the x-axis as
requested in EHP Request 1. Also, we show in Figures \@ref(fig:fig3check1) and
\@ref(fig:fig3check2) of this response how the revised Figure 3 would look with
three common types of color blindness as well as when printed in black and
white. The gradient is clear when this figure is printed in black and white.

```{r fig3check1, fig.cap="Reproduction of revised version of Figure 3 to check accessibility to readers with two types of colorblindness, deuteranopia (left) and protanopia (right).", out.width="100%"}
include_graphics("figures/windcomparison_check1.pdf")
```

```{r fig3check2, fig.cap="Reproduction of revised version of Figure 3 to check accessibility to readers with a third type of colorblindness, tritanopia (left) and for printing the figure in grayscale (right).", out.width="100%"}
include_graphics("figures/windcomparison_check2.pdf")
```

\begin{shaded}
\textbf{EHP Request 4:}
Figure 4: Even with nominally normal color vision and a large high-resolution
monitor, it is difficult for me to make out the color differences in the
symbols-- almost all appear black or very dark blue, a dozen or so look yellow,
and a handful look dark grey. Is there any way to increase the contrast in these
colors? Would you consider binning into categories instead of using a
continuous color gradient?
\end{shaded}

@@

**Response:**

\begin{shaded}
\textbf{EHP Request 5:}
Figures 5--6: Please check to see if the colors used can be distinguished if
printed in black and white, and if not, use a “color-blind friendly” palette if
possible. If this is not feasible, we can request and exemption from
accessibility requirements, but we try to do this only when alternatives  would
degrade the information content of  the figure.
\end{shaded}

@@

**Response:**

As we explain in our response to EHP Request 2, these figures' color palette is
color-blind friendly and also remains perceptible when printed in grayscale.
Figures \@ref(fig:fig5check1) and \@ref(fig:fig5check1) show what Figure 5 would
look like under three common types of color blindness and when printed in black
and white. Figures \@ref(fig:fig6check1) and \@ref(fig:fig6check2) show the same
thing for Figure 6. Therefore, these figures should not require any exemption
from accessibility requirements, as they should satisfy these requirements.

```{r fig6check1, fig.cap="Reproduction of revised version of Figure 6 to check accessibility to readers with two types of colorblindness, deuteranopia (left) and protanopia (right).", fig.show = "hold", out.width="50%"}
include_graphics("figures/jaccard_heatmap_check1.pdf")

include_graphics("figures/jaccard_heatmap_check2.pdf")
```

```{r fig6check2, fig.cap="Reproduction of revised version of Figure 6 to check accessibility to readers with a third type of colorblindness, tritanopia (left) and for printing the figure in grayscale (right).", fig.show = "hold", out.width="50%"}
include_graphics("figures/jaccard_heatmap_check3.pdf")
include_graphics("figures/jaccard_heatmap_check4.pdf")
```

@@

\begin{shaded}
\textbf{R2 Comment 6:}
Supplemental Material: Please provide your supplemental material file in Word
(.docx) format. For additional information, see:
\url{https://ehp.niehs.nih.gov/authors/supplemental-material}. \end{shaded}

**Response:**

We have provided the Supplemental Material in the Word file format in our
revised submission.

### 2020-07-21 ehp_revision/writing/ehp_introduction.tex
Work some more on revisions

Further, when studies use distance from the storm's track to assess exposure,
they often use the same buffer constraints on each side of the storm track
(e.g.,~\cite{kinney2008, currie2013}).  However, the forces of a tropical
cyclone tend to be distributed around its center non-symmetrically.  \textbf{In
the Northern Hemisphere,} extreme winds are more common to the track's right,
where counterclockwise cyclonic winds move in concert with the tropical
cyclone's forward motion~\parencite{halverson2015}, and almost all of the fatal
tornadoes associated with \ac{US} tropical cyclones between~1995 and~2009
occurred to the right of the tropical cyclone's track~\parencite{moore2012}.
Rain, conversely, is often heaviest to the left of the track, especially when
the tropical cyclone interacts with other weather
systems~\parencite{atallah2003, atallah2007, zhu2013variations} or undergoes an
extratropical transition~\parencite{elsberry2002}.

>>>>

Further, when studies use distance from the storm's track to assess exposure,
they often use the same buffer constraints on each side of the storm track
(e.g.,~\cite{kinney2008, currie2013}).  However, the forces of a tropical
cyclone tend to be distributed around its center non-symmetrically.  \textbf{In
the Northern Hemisphere, cyclonic winds are counterclockwise,} so extreme
winds are more common to the track's right where cyclonic winds move in
concert with the tropical cyclone's forward motion. extreme winds are more
common to the track's right, where counterclockwise cyclonic winds move in
concert with the tropical cyclone's forward motion~\parencite{halverson2015},
and almost all of the fatal tornadoes associated with \ac{US} tropical cyclones
between~1995 and~2009 occurred to the right of the tropical cyclone's
track~\parencite{moore2012}.  Rain, conversely, is often heaviest to the left
of the track, especially when the tropical cyclone interacts with other weather
systems~\parencite{atallah2003, atallah2007, zhu2013variations} or undergoes an
extratropical transition~\parencite{elsberry2002}.

### 2020-07-21 ehp_revision/writing/ehp_methods.tex
Work some more on revisions

We first measured how close each storm's central track came to each county. We
used tracking data from \ac{HURDAT2}, which records the storm center's position
at four standardized times for weather data collection (synoptic times),
6:00~am, 12:00~pm, 6:00~pm, and 12:00~am \ac{UTC}.  We interpolated this
position to~15-\si{\minute} intervals using natural cubic spline
interpolation~\parencite{hurricaneexposure}. At each~15-\si{\minute} interval,
we measured the distance between the storm's center and each county's
population mean center~\parencite{countycenters}. We took the minimum distance
for each county as a measure of how close the storm came to the county over its
lifetime.  We also recorded the time when this occurred for each county so we
could later link observed data on precipitation, flooding, and tornadoes.  To
allow matching with data recorded in local time (e.g., health data), we
converted these times from \ac{UTC} to local time~\parencite{countytimezones}.

>>>>

We first measured how close each storm's central track came to each county. We
used tracking data from \ac{HURDAT2}, which records the storm center's position
at four standardized times for weather data collection (synoptic times),
6:00~am, 12:00~pm, 6:00~pm, and 12:00~am \ac{UTC}.  We interpolated this
position to~15-\si{\minute} intervals using natural cubic spline
interpolation~\parencite{hurricaneexposure}. At each~15-\si{\minute} interval,
we measured the distance between the storm's center and each county's
population mean center, **as of the 2010 US Decennial Census**~\parencite{countycenters}. We took the minimum distance
for each county as a measure of how close the storm came to the county over its
lifetime.  We also recorded the time when this occurred for each county so we
could later link observed data on precipitation, flooding, and tornadoes.  To
allow matching with data recorded in local time (e.g., health data), we
converted these times from \ac{UTC} to local time~\parencite{countytimezones}.
